Reading Notes

### 2020-07-27 reading-notes.tex
reading and writing, mostly organizing cleanup

\cite{Paul1995a}
\cite{Yang2006a}
\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

\cite{Paul1995a}

united atom model for alkane chain melts. terminal methyl has deeper well than internal methylene groups. compared to experiments and all-atom model. good agreement for phase behavior, chain conformations, x-ray scattering profiles. Large-scale dynamics like self-diffusion agree with experiment and are 30\% faster!
first intro paragraph really concise c: remind us about the difficulty in selecting a model and there are many competing model for a system as simple as n-alkanes.

\cite{Yang2006a}
\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
